SIR Model with Testing and Isolation Mechanisms

### 2020-11-10 codes/ali_test_sir.Rmd
update plots and prep notes

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_t <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011
 W_S <- .3 #choose 0.3 for TTI testing plan and 1 for the random testing.

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p1
    + geom_contour_filled(breaks=pretty(unique(df2$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
)
```

@@

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
)
```

>>>>

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_t <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011
 W_S <- 0.3 #choose 0.3 for TTI testing plan and 1 for the random testing.

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
p1_temp <- (p1
    + geom_contour_filled(breaks=pretty(unique(df2$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle("W[S]=0.3, W[I]=W[R]=1")
)
p1_temp
# filename = "R0contour_TTI.png"
# filename = "R0contour_random.png"
ggsave(p1_temp,filename = "R0contour_TTI.png" , path="../pix/")
```

@@

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle("W[S]=0.3, W[I]=W[R]=1")
)
```

### 2020-11-10 note/SIR_notes.Rnw
update analysis of R0 wrt omega
update plots and prep notes

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}
\bibliographystyle{apalike}

@@

% %%%%%%%
\section{Method}

% %%%%%%%
\section{Analysis}

\section{Literature Review}

% %%%%%%%
\subsection{Explicit models of TTI (trace/test/isolate) based on network or agent-based models}

@@

\citep{elbanna2020entry} [seems similar to MacPan model!]
% %%%%%%%
\subsection{Models of repeated random testing of isolated populations}
\cite{bergstrom2020frequency}
(1) Model, assumptions: They developed a function, namely expected expoisour $E(C,\tau)$, to approximate trade-offs between the frequency of testing, n, the sensitivity of testing, q, and the delay between
testing and results, d. This function is explicitly derived and was connected the effective reproduction number $R=R_0 S$, where $S$ is the proportion of population susciptable.
assumption that transmission rates are a step function: individuals who
have COVID go from non-infectious to fully infectious instantaneously,
and remain fully infectious until they are no longer able to transmit disease. Test sensitivity takes the same form over the course of infection.
More sophisticated models could allow varying infectiousness and varying
sensitivity over time, as in 
\citep{larremore2020test}.

>>>>

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\bibliographystyle{apalike}

@@

% %%%%%%%
\section{Method}
- $\Lambda$: force of infection defined as $$\Lambda=\beta \frac{(I_u+\eta_w I_n+\eta_w I_p+ \eta_t I_t)}{N_0},$$ where $\beta$ is transmission rate, $\eta_w$ and $\eta_t$ are the isolation parameters for awaiting and reported individuals, respectively. We assume that $\eta_t<\eta_w$, i.e., the awaiting individuals for test results have a higher transmission probability than the reported individuals.
- $\omega$: the rate of *onward flow* from the awaiting positive compartment, $p$, to reported/tested compartment, $\rho$, or from awaiting negative compartment, $n$, back to $u$.  It has units of $1/time$.
- $\gamma$: recovery rate ($1/time$).
- $\rho$: per capita testing intensity across the whole population ($1/time$).
- $W$: weighted number of people available for tests, defined as $W = W_S S_u + W_I I_u + W_R R_u$.
- $\sigma$: scaling parameter for testing defined as $\sigma = \frac{\rho N_0}{W}$.
- $F_Z$: Weighted testing rate defined as $F_Z=\sigma W_Z$. That is, $F_S = \sigma W_S$, $F_I=\sigma W_I$ and $F_R = \sigma W_R$.

\includegraphics[width=\linewidth]{../pix/sir_comp2.png}

% %%%%%%%
\section{Results}

\newpage
\begin{figure}
\centering
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{../pix/R0contour_random.png}
        \caption{}\label{fig:fig_a}
\end{subfigure}
%
\begin{subfigure}[t]{.45\textwidth}
\centering
\includegraphics[width=\linewidth]{../pix/R0contour_TTI.png}
\caption{}\label{fig:fig_b}
\end{subfigure}
\end{figure}

% %%%%%%%
\section{Thoughts/Objectives}

\begin{enumerate}
\item aa
\end{enumerate}

% %%%%%%%
\section{Literature Review}

\subsection{Explicit models of TTI (trace/test/isolate) based on network or agent-based models}

@@

\citep{elbanna2020entry} [seems similar to MacPan model!]

\citep{de2020influenza} Was discussed in the Math 747 
SEIR Asymptomatic and symptomatic $I_1, I_2$. Used linear chain trick 
Stringency index as a control force lowering $\beta$.

\citep{rice2020effect} Effect of school closures on mortality. Reproduce Report 9 results by spatial agent based CovidSim. 
% %%%%%%%
\subsection{Models of repeated random testing of isolated populations}
\cite{bergstrom2020frequency}
(1) Model, assumptions: They developed a function, namely expected expoisour $E(C,\tau)$, to approximate trade-offs between the frequency of testing, n, the sensitivity of testing, q, and the delay between
testing and results, d. This function is explicitly derived and was connected the effective reproduction number $R=R_0 S$, where $S$ is the proportion of population susciptable.
assumption that transmission rates are a step function: individuals who
have COVID go from non-infectious to fully infectious instantaneously,
and remain fully infectious until they are no longer able to transmit disease. Test sensitivity takes the same form over the course of infection.
More sophisticated models could allow varying infectiousness and varying
sensitivity over time, as in 
\citep{larremore2020test}.
